---
title: "Final_Exam_Q11"
author: "Purvesh"
date: "5/7/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(car)
library(leaps)
library(qqplotr)
library(alr3)
library(olsrr)
```
```{r}
view(galapagos)
```

# Galapahos is the dataset which consists following variables which are mentioned below: 

NS
Number of Species

ES
Number of endemic species (orrur only on that island)

Area
Surface area of island, hectares

Anear
Area of closest island, hectares

Dist
Distance to closest island, km

DistSC
Distance from Santa Cruz Island, km

Elevation
Elevation in m, missing values given as zero

EM
1 if elevation is observed, 0 if missing 

# section a.

In this section we are asked to perform MLR to investigate relationship.
here, It is observed that Number of endemic species is the most significant and if we see at overall model P value is 1.075e-09 which is good. 
R-squared:  0.9525,	Adjusted R-squared:  0.9346 
here we can observe that individual variables are not good in value, it means there is colinearity(see colinearity below)
Apart from regression Residual and influence plot is plotted where we can observe the influncing points and different plots.
In residual vs leverage graph we can see "Isabela" is affecting the model.

```{r}
model<-lm(NS~., data=galapagos)
par(mfrow=c(2,2))
summary(model)
modeladj.r2 = summary(model)$adj.r.squared
model.r2 = summary(model)$r.squared
plot(model)
influenceIndexPlot(model)
```

```{r}
cor(galapagos)
```
```{r}
model.step = lm(NS~., data =galapagos)
ols_step_forward_p(model.step)
ols_step_both_p(model.step )
```


# Section b.

In this we are asked to perform Trransformation. As we can see in the previous section Residual plots, Best transformation we can fit here is BOXCOX, with BoxCox we got lambda value = 0.5858586. This value will be used for transformation in the model.
After performing the transformation, it is observed that: 
R-squared:  0.9685,	Adjusted R-squared:  0.9566 is increased from the previous  untransformed model.
p-value: 4.153e-11 there is changes in P value as well, which tells transformation is good for the model.
one more thing is to observe residual plots are changed and much better than the untranformed model. cook's distance much more in Residual and Leverage plot and we can check same things in influence plot.
After this, graphical representation is done for the adj R square as well with untransformed and transformed model.

```{r}
bxmodel <- boxCox(model)
lambda <- bxmodel$x[which.max(bxmodel$y)]
lambda
```

```{r}
Tmodel<- lm(NS^(0.5858586)~., data = galapagos)
par(mfrow=c(2,2))
summary(Tmodel)
Tmodeladj.r2 = summary(Tmodel)$adj.r.squared
Tmodel.r2 = summary(Tmodel)$r.squared
plot(Tmodel)
influenceIndexPlot(Tmodel)
```
```{r}
Tmodel.full = lm(NS^(0.5858586)~., data = galapagos)
ols_step_forward_p(Tmodel.full)
ols_step_both_p(Tmodel.full )
```

```{r}
notquiteall.models =regsubsets(NS~., data = galapagos, nbest = 1 ) 
plot(notquiteall.models, scale = "adjr2")
```
```{r}
notquiteall.Tmodels =regsubsets(NS^(0.5858586)~., data = galapagos, nbest = 1 ) 
plot(notquiteall.Tmodels, scale = "adjr2")
```
```{r}
regsubsets(NS^(0.5858586)~.,data= galapagos, nbest = 3) -> all.models 
summary(all.models) -> summ
summ
```

# Section c.

Here is the chart comparision of results before and after transformation in R-square and Adj R-square.


```{r}
results = data.frame(modeladj.r2, Tmodeladj.r2,model.r2,Tmodel.r2)
round(results,3)
```


